Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-17 jss/article.tex
Added ref of figures
[skip ci]
[skip ci] jss update

The package also includes a use-case that we detail below. Using,
\code{genes_test} it is possible to explore the different possibilities of
exploration of the maps. We previously computed the p-value of
\code{genes_test} with default parameters.  The number of modules which have a
p-value below 0.05 was 36, that can be compared to the 49 obtained without
correction: \code{enrichment(genes_test,correction_multitest = FALSE)}

@@

We can now plot the first ten rows of the results obtained for corrected and uncorrected fisher test (figure 1).

\begin{figure}
	\centering
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction or no correction. Grey tiles means that the data is not available for this module in this sample. P-values of low significance are in white, whereas p-values of high significance are represent in blue. Samples are in abscissa and modules are on the Y axis  }
	\includegraphics{figures/comparison_corrected_unc.pdf}
\end{figure}

\begin{figure}
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction (left) or no correction (right). The modules are on the X axis and the p-values are on the Y axis.  }
	\includegraphics{figures/comparison_corrected_unc_bars.pdf}
\end{figure}

>>>>

We previously computed the p-value of the \code{genes_test} list with default
parameters. The number of modules which have a p-value below 0.05 was 36, that
can be compared to the 49 obtained without correction with the simple command
shown below (some of the results are displayed in table \ref{tab:table2}).

\begin{verbatim}
enrichment(genes_test,correction_multitest = FALSE)
\end{verbatim}

@@

We can now plot the first ten rows of the results obtained for corrected and uncorrected fisher test with heatmap format (Figure~\ref{fig:heatm}) or barplot (Figure~\ref{fig:barp}).

\begin{figure}
	\centering
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction or no correction. Grey tiles means that the data is not available for this module in this sample. P-values of low significance are in white, whereas p-values of high significance are represent in blue. Samples are in abscissa and modules are on the Y axis  }
	\includegraphics{figures/comparison_corrected_unc.pdf}
    \label{fig:heatm}

\end{figure}

\begin{figure}
	\caption{Representation of the enriched modules (first ten rows), either with either Bonferroni correction (left) or no correction (right). The modules are on the X axis and the p-values are on the Y axis.  }
	\includegraphics{figures/comparison_corrected_unc_bars.pdf}
	\label{fig:barp}

\end{figure}
